---
title: "DC Hypothesis Tests"
author: "Jacob Prince"
date: "2023-03-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Total Era Tests
```{r}
library(readxl)
eraTotals <- read_excel("EraCompare.xlsx")
#View(eraTotals)
AoCUnits <- eraTotals$`Age of Crisis Units`
New52Units <- eraTotals$`DC New 52 Units`
RebirthUnits <- eraTotals$`DC Rebirth Units`
```
Test Between AoC Total Units vs New 52 Total Units
```{r}
t.test(AoCUnits,New52Units, alternative="two.sided", conf.level=0.95,paired = FALSE)
```
Test Between New 52 Total Units vs Rebirth Total Units
```{r}
t.test(New52Units,RebirthUnits, alternative="two.sided", conf.level=0.95,paired = FALSE)
```

## Change of Era Tests
```{r}
library(readxl)
new52Changes <- read_excel("New52Switch.xlsx")
rebirthChanges <- read_excel("RebirthSwitch.xlsx")
#View(new52Changes)
#View(rebirthChanges)
a_n1a <- new52Changes$AoC1
a_n1n <- new52Changes$New1
a_n2a <- new52Changes$AoC2
a_n2n <- new52Changes$New2
n_r1n <- rebirthChanges$New1
n_r1r <- rebirthChanges$Rebirth1
n_r2n <- rebirthChanges$New2
n_r2r <- rebirthChanges$Rebirth2
```

One Year Test (Age of Crisis to New 52)
```{r}
t.test(a_n1a,a_n1n, alternative="two.sided", conf.level=0.95,paired = FALSE)
```
Two Year Test (Age of Crisis to New 52)
```{r}
t.test(a_n2a,a_n2n, alternative="two.sided", conf.level=0.95,paired = FALSE)
```
One Year Test (New 52 to Rebirth)
```{r}
t.test(n_r1n,n_r1r, alternative="two.sided", conf.level=0.95,paired = FALSE)
```

Two Year Test (New 52 to Rebirth)
```{r}
t.test(n_r2n,n_r2r, alternative="two.sided", conf.level=0.95,paired = FALSE)
```
## Comic Appearances (2008-2020)
Whole Time Period
```{r}
library(readxl)
comicsIn <- read_excel("CharacterComicsIn.xlsx")
#View(comicsIn)
BatmanIn <- comicsIn$Batman
SupermanIn <- comicsIn$Superman
Top5 <- c(comicsIn$Superman,comicsIn$`Wonder Woman`,comicsIn$`Flash (Barry)`,comicsIn$Nightwing)
allChar <- c(comicsIn$Superman,comicsIn$`Wonder Woman`,comicsIn$`Flash (Barry)`,comicsIn$Nightwing,comicsIn$Aquaman,comicsIn$`Flash (Wally)`,comicsIn$`Green Lantern (Hal)`,comicsIn$`Martian Manhunter`,comicsIn$Shazam,comicsIn$`Green Arrow`,comicsIn$Cyborg,comicsIn$Supergirl,comicsIn$Hawkman,comicsIn$`Green Lantern (John)`,comicsIn$`Green Lantern (Kyle)`,comicsIn$`Black Canary`,comicsIn$Batgirl,comicsIn$Zatanna,comicsIn$`John Constantine`,comicsIn$Starfire,comicsIn$`Dr Fate`,comicsIn$`Blue Beetle (Jaime)`,comicsIn$`Booster Gold`,comicsIn$`Swamp Thing`,comicsIn$Joker,comicsIn$`Lex Luthor`,comicsIn$`Harley Quinn`,comicsIn$Deathstroke,comicsIn$Catwoman)
t.test(BatmanIn, SupermanIn, alternative="two.sided", conf.level=0.95,paired = FALSE)
t.test(BatmanIn, Top5, alternative="two.sided", conf.level=0.95,paired = FALSE)
t.test(BatmanIn, allChar, alternative="two.sided", conf.level=0.95,paired = FALSE)
```


## Comic Appearances (Age of Crisis End)
```{r}
comicsIn <- read_excel("AoCComicsIn.xlsx")
#View(comicsIn)
BatmanIn <- comicsIn$Batman
SupermanIn <- comicsIn$Superman
Top5 <- c(comicsIn$Superman,comicsIn$`Wonder Woman`,comicsIn$`Flash (Barry)`,comicsIn$Nightwing)
allChar <- c(comicsIn$Superman,comicsIn$`Wonder Woman`,comicsIn$`Flash (Barry)`,comicsIn$Nightwing,comicsIn$Aquaman,comicsIn$`Flash (Wally)`,comicsIn$`Green Lantern (Hal)`,comicsIn$`Martian Manhunter`,comicsIn$Shazam,comicsIn$`Green Arrow`,comicsIn$Cyborg,comicsIn$Supergirl,comicsIn$Hawkman,comicsIn$`Green Lantern (John)`,comicsIn$`Green Lantern (Kyle)`,comicsIn$`Black Canary`,comicsIn$Batgirl,comicsIn$Zatanna,comicsIn$`John Constantine`,comicsIn$Starfire,comicsIn$`Dr Fate`,comicsIn$`Blue Beetle (Jaime)`,comicsIn$`Booster Gold`,comicsIn$`Swamp Thing`,comicsIn$Joker,comicsIn$`Lex Luthor`,comicsIn$`Harley Quinn`,comicsIn$Deathstroke,comicsIn$Catwoman)
t.test(BatmanIn, SupermanIn, alternative="two.sided", conf.level=0.95,paired = FALSE)
t.test(BatmanIn, Top5, alternative="two.sided", conf.level=0.95,paired = FALSE)
t.test(BatmanIn, allChar, alternative="two.sided", conf.level=0.95,paired = FALSE)
```
## Comic Appearances (New 52)
```{r}
comicsIn <- read_excel("New52ComicsIn.xlsx")
#View(comicsIn)
BatmanIn <- comicsIn$Batman
SupermanIn <- comicsIn$Superman
Top5 <- c(comicsIn$Superman,comicsIn$`Wonder Woman`,comicsIn$`Flash (Barry)`,comicsIn$Nightwing)
allChar <- c(comicsIn$Superman,comicsIn$`Wonder Woman`,comicsIn$`Flash (Barry)`,comicsIn$Nightwing,comicsIn$Aquaman,comicsIn$`Flash (Wally)`,comicsIn$`Green Lantern (Hal)`,comicsIn$`Martian Manhunter`,comicsIn$Shazam,comicsIn$`Green Arrow`,comicsIn$Cyborg,comicsIn$Supergirl,comicsIn$Hawkman,comicsIn$`Green Lantern (John)`,comicsIn$`Green Lantern (Kyle)`,comicsIn$`Black Canary`,comicsIn$Batgirl,comicsIn$Zatanna,comicsIn$`John Constantine`,comicsIn$Starfire,comicsIn$`Dr Fate`,comicsIn$`Blue Beetle (Jaime)`,comicsIn$`Booster Gold`,comicsIn$`Swamp Thing`,comicsIn$Joker,comicsIn$`Lex Luthor`,comicsIn$`Harley Quinn`,comicsIn$Deathstroke,comicsIn$Catwoman)
t.test(BatmanIn, SupermanIn, alternative="two.sided", conf.level=0.95,paired = FALSE)
t.test(BatmanIn, Top5, alternative="two.sided", conf.level=0.95,paired = FALSE)
t.test(BatmanIn, allChar, alternative="two.sided", conf.level=0.95,paired = FALSE)
```
## Comic Appearances (Rebirth)
```{r}
comicsIn <- read_excel("RebirthComicsIn.xlsx")
#View(comicsIn)
BatmanIn <- comicsIn$Batman
SupermanIn <- comicsIn$Superman
Top5 <- c(comicsIn$Superman,comicsIn$`Wonder Woman`,comicsIn$`Flash (Barry)`,comicsIn$Nightwing)
allChar <- c(comicsIn$Superman,comicsIn$`Wonder Woman`,comicsIn$`Flash (Barry)`,comicsIn$Nightwing,comicsIn$Aquaman,comicsIn$`Flash (Wally)`,comicsIn$`Green Lantern (Hal)`,comicsIn$`Martian Manhunter`,comicsIn$Shazam,comicsIn$`Green Arrow`,comicsIn$Cyborg,comicsIn$Supergirl,comicsIn$Hawkman,comicsIn$`Green Lantern (John)`,comicsIn$`Green Lantern (Kyle)`,comicsIn$`Black Canary`,comicsIn$Batgirl,comicsIn$Zatanna,comicsIn$`John Constantine`,comicsIn$Starfire,comicsIn$`Dr Fate`,comicsIn$`Blue Beetle (Jaime)`,comicsIn$`Booster Gold`,comicsIn$`Swamp Thing`,comicsIn$Joker,comicsIn$`Lex Luthor`,comicsIn$`Harley Quinn`,comicsIn$Deathstroke,comicsIn$Catwoman)
t.test(BatmanIn, SupermanIn, alternative="two.sided", conf.level=0.95,paired = FALSE)
t.test(BatmanIn, Top5, alternative="two.sided", conf.level=0.95,paired = FALSE)
t.test(BatmanIn, allChar, alternative="two.sided", conf.level=0.95,paired = FALSE)
```