---
title: "DC Hypothesis Tests"
author: "Jacob Prince"
date: "2023-03-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Total Era Tests
```{r}
library(readxl)
eraTotals <- read_excel("EraCompare.xlsx")
#View(eraTotals)
AoCUnits <- eraTotals$`Age of Crisis Units`
New52Units <- eraTotals$`DC New 52 Units`
RebirthUnits <- eraTotals$`DC Rebirth Units`
```
Test Between AoC Total Units vs New 52 Total Units
```{r}
t.test(AoCUnits,New52Units, alternative="two.sided", conf.level=0.95,paired = FALSE)
```
Test Between New 52 Total Units vs Rebirth Total Units
```{r}
t.test(New52Units,RebirthUnits, alternative="two.sided", conf.level=0.95,paired = FALSE)
```

## Change of Era Tests
```{r}
library(readxl)
new52Changes <- read_excel("New52Switch.xlsx")
rebirthChanges <- read_excel("RebirthSwitch.xlsx")
#View(new52Changes)
#View(rebirthChanges)
a_n1a <- new52Changes$AoC1
a_n1n <- new52Changes$New1
a_n2a <- new52Changes$AoC2
a_n2n <- new52Changes$New2
n_r1n <- rebirthChanges$New1
n_r1r <- rebirthChanges$Rebirth1
n_r2n <- rebirthChanges$New2
n_r2r <- rebirthChanges$Rebirth2
```

One Year Test (Age of Crisis to New 52)
```{r}
t.test(a_n1a,a_n1n, alternative="two.sided", conf.level=0.95,paired = FALSE)
```
Two Year Test (Age of Crisis to New 52)
```{r}
t.test(a_n2a,a_n2n, alternative="two.sided", conf.level=0.95,paired = FALSE)
```
One Year Test (New 52 to Rebirth)
```{r}
t.test(n_r1n,n_r1r, alternative="two.sided", conf.level=0.95,paired = FALSE)
```

Two Year Test (New 52 to Rebirth)
```{r}
t.test(n_r2n,n_r2r, alternative="two.sided", conf.level=0.95,paired = FALSE)
```
## Comic Appearances (2008-2020)
Whole Time Period
```{r}
library(readxl)
comicsIn <- read_excel("CharacterComicsIn.xlsx")
#View(comicsIn)
BatmanIn <- comicsIn$Batman
SupermanIn <- comicsIn$Superman
Top5 <- c(comicsIn$Superman,comicsIn$`Wonder Woman`,comicsIn$`Flash (Barry)`,comicsIn$Nightwing)
allChar <- c(comicsIn$Superman,comicsIn$`Wonder Woman`,comicsIn$`Flash (Barry)`,comicsIn$Nightwing,comicsIn$Aquaman,comicsIn$`Flash (Wally)`,comicsIn$`Green Lantern (Hal)`,comicsIn$`Martian Manhunter`,comicsIn$Shazam,comicsIn$`Green Arrow`,comicsIn$Cyborg,comicsIn$Supergirl,comicsIn$Hawkman,comicsIn$`Green Lantern (John)`,comicsIn$`Green Lantern (Kyle)`,comicsIn$`Black Canary`,comicsIn$Batgirl,comicsIn$Zatanna,comicsIn$`John Constantine`,comicsIn$Starfire,comicsIn$`Dr Fate`,comicsIn$`Blue Beetle (Jaime)`,comicsIn$`Booster Gold`,comicsIn$`Swamp Thing`,comicsIn$Joker,comicsIn$`Lex Luthor`,comicsIn$`Harley Quinn`,comicsIn$Deathstroke,comicsIn$Catwoman)
t.test(BatmanIn, SupermanIn, alternative="greater", conf.level=0.95,paired = FALSE)
t.test(BatmanIn, Top5, alternative="greater", conf.level=0.95,paired = FALSE)
t.test(BatmanIn, allChar, alternative="greater", conf.level=0.95,paired = FALSE)
```


## Comic Appearances (Age of Crisis End)
```{r}
comicsIn <- read_excel("AoCComicsIn.xlsx")
#View(comicsIn)
BatmanIn <- comicsIn$Batman
SupermanIn <- comicsIn$Superman
Top5 <- c(comicsIn$Superman,comicsIn$`Wonder Woman`,comicsIn$`Flash (Barry)`,comicsIn$Nightwing)
allChar <- c(comicsIn$Superman,comicsIn$`Wonder Woman`,comicsIn$`Flash (Barry)`,comicsIn$Nightwing,comicsIn$Aquaman,comicsIn$`Flash (Wally)`,comicsIn$`Green Lantern (Hal)`,comicsIn$`Martian Manhunter`,comicsIn$Shazam,comicsIn$`Green Arrow`,comicsIn$Cyborg,comicsIn$Supergirl,comicsIn$Hawkman,comicsIn$`Green Lantern (John)`,comicsIn$`Green Lantern (Kyle)`,comicsIn$`Black Canary`,comicsIn$Batgirl,comicsIn$Zatanna,comicsIn$`John Constantine`,comicsIn$Starfire,comicsIn$`Dr Fate`,comicsIn$`Blue Beetle (Jaime)`,comicsIn$`Booster Gold`,comicsIn$`Swamp Thing`,comicsIn$Joker,comicsIn$`Lex Luthor`,comicsIn$`Harley Quinn`,comicsIn$Deathstroke,comicsIn$Catwoman)
t.test(BatmanIn, SupermanIn, alternative="greater", conf.level=0.95,paired = FALSE)
t.test(BatmanIn, Top5, alternative="greater", conf.level=0.95,paired = FALSE)
t.test(BatmanIn, allChar, alternative="greater", conf.level=0.95,paired = FALSE)
```
## Comic Appearances (New 52)
```{r}
comicsIn <- read_excel("New52ComicsIn.xlsx")
#View(comicsIn)
BatmanIn <- comicsIn$Batman
SupermanIn <- comicsIn$Superman
Top5 <- c(comicsIn$Superman,comicsIn$`Wonder Woman`,comicsIn$`Flash (Barry)`,comicsIn$Nightwing)
allChar <- c(comicsIn$Superman,comicsIn$`Wonder Woman`,comicsIn$`Flash (Barry)`,comicsIn$Nightwing,comicsIn$Aquaman,comicsIn$`Flash (Wally)`,comicsIn$`Green Lantern (Hal)`,comicsIn$`Martian Manhunter`,comicsIn$Shazam,comicsIn$`Green Arrow`,comicsIn$Cyborg,comicsIn$Supergirl,comicsIn$Hawkman,comicsIn$`Green Lantern (John)`,comicsIn$`Green Lantern (Kyle)`,comicsIn$`Black Canary`,comicsIn$Batgirl,comicsIn$Zatanna,comicsIn$`John Constantine`,comicsIn$Starfire,comicsIn$`Dr Fate`,comicsIn$`Blue Beetle (Jaime)`,comicsIn$`Booster Gold`,comicsIn$`Swamp Thing`,comicsIn$Joker,comicsIn$`Lex Luthor`,comicsIn$`Harley Quinn`,comicsIn$Deathstroke,comicsIn$Catwoman)
t.test(BatmanIn, SupermanIn, alternative="greater", conf.level=0.95,paired = FALSE)
t.test(BatmanIn, Top5, alternative="greater", conf.level=0.95,paired = FALSE)
t.test(BatmanIn, allChar, alternative="greater", conf.level=0.95,paired = FALSE)
```
## Comic Appearances (Rebirth)
```{r}
comicsIn <- read_excel("RebirthComicsIn.xlsx")
#View(comicsIn)
BatmanIn <- comicsIn$Batman
SupermanIn <- comicsIn$Superman
Top5 <- c(comicsIn$Superman,comicsIn$`Wonder Woman`,comicsIn$`Flash (Barry)`,comicsIn$Nightwing)
allChar <- c(comicsIn$Superman,comicsIn$`Wonder Woman`,comicsIn$`Flash (Barry)`,comicsIn$Nightwing,comicsIn$Aquaman,comicsIn$`Flash (Wally)`,comicsIn$`Green Lantern (Hal)`,comicsIn$`Martian Manhunter`,comicsIn$Shazam,comicsIn$`Green Arrow`,comicsIn$Cyborg,comicsIn$Supergirl,comicsIn$Hawkman,comicsIn$`Green Lantern (John)`,comicsIn$`Green Lantern (Kyle)`,comicsIn$`Black Canary`,comicsIn$Batgirl,comicsIn$Zatanna,comicsIn$`John Constantine`,comicsIn$Starfire,comicsIn$`Dr Fate`,comicsIn$`Blue Beetle (Jaime)`,comicsIn$`Booster Gold`,comicsIn$`Swamp Thing`,comicsIn$Joker,comicsIn$`Lex Luthor`,comicsIn$`Harley Quinn`,comicsIn$Deathstroke,comicsIn$Catwoman)
t.test(BatmanIn, SupermanIn, alternative="greater", conf.level=0.95,paired = FALSE)
t.test(BatmanIn, Top5, alternative="greater", conf.level=0.95,paired = FALSE)
t.test(BatmanIn, allChar, alternative="greater", conf.level=0.95,paired = FALSE)
```

## Comic Sales 
```{r}
library(readxl)
charSales <- read_excel("CharacterSales.xlsx")
AoCSales <- read_excel("AoCCharacterSales.xlsx")
new52Sales <- read_excel("New52CharacterSales.xlsx")
new52SalesSwitch <- read_excel("New52SwitchSales.xlsx")
new52Sales1Switch <- read_excel("New52Switch1Sales.xlsx")
RebirthSales <- read_excel("RebirthCharacterSales.xlsx")
RebirthSalesSwitch <- read_excel("RebirthSwitchSales.xlsx")
RebirthSales1Switch <- read_excel("RebirthSwitch1Sales.xlsx")
#View(new52SalesSwitch)
```

```{r}
BatmanSales <- charSales$Batman
SupermanSales <- charSales$Superman
WonderWomanSales <- charSales$`Wonder Woman`
FlashSales <- charSales$`Flash (Barry)`
NightwingSales <- charSales$Nightwing
Top5Sales <- c(WonderWomanSales,SupermanSales,FlashSales,NightwingSales)
t.test(BatmanSales, SupermanSales, alternative="two.sided", conf.level=0.95,paired = FALSE)
t.test(BatmanSales, WonderWomanSales, alternative="two.sided", conf.level=0.95,paired = FALSE)
t.test(BatmanSales, FlashSales, alternative="two.sided", conf.level=0.95,paired = FALSE)
t.test(BatmanSales, NightwingSales, alternative="two.sided", conf.level=0.95,paired = FALSE)
t.test(BatmanSales, Top5Sales, alternative="two.sided", conf.level=0.95,paired = FALSE)
```

```{r}
BatmanAoCSales <- AoCSales$Batman
SupermanAoCSales <- AoCSales$Superman
WonderWomanAoCSales <- AoCSales$`Wonder Woman`
FlashAoCSales <- AoCSales$`Flash (Barry)`
NightwingAoCSales <- AoCSales$Nightwing
BatmanNew52Sales <- new52Sales$Batman
SupermanNew52Sales <- new52Sales$Superman
WonderWomanNew52Sales <- new52Sales$`Wonder Woman`
FlashNew52Sales <- new52Sales$`Flash (Barry)`
NightwingNew52Sales <- new52Sales$Nightwing
BatmanRebirthSales <- RebirthSales$Batman
SupermanRebirthSales <- RebirthSales$Superman
WonderWomanRebirthSales <- RebirthSales$`Wonder Woman`
FlashRebirthSales <- RebirthSales$`Flash (Barry)`
NightwingRebirthSales <- RebirthSales$Nightwing
BatmanNew52Switch <- new52SalesSwitch$Batman
BatmanNew52Switch2 <- new52SalesSwitch$`Batman 2`
SupermanNew52Switch <- new52SalesSwitch$Superman
SupermanNew52Switch2 <- new52SalesSwitch$`Superman 2`
WonderWomanNew52Switch <- new52SalesSwitch$`Wonder Woman`
WonderWomanNew52Switch2 <- new52SalesSwitch$`Wonder Woman 2`
FlashNew52Switch <- new52SalesSwitch$`Flash (Barry)`
FlashNew52Switch2 <- new52SalesSwitch$`Flash (Barry) 2`
NightwingNew52Switch <- new52SalesSwitch$Nightwing
NightwingNew52Switch2 <- new52SalesSwitch$`Nightwing 2`
BatmanRebirthSwitch <- RebirthSalesSwitch$Batman
BatmanRebirthSwitch2 <- RebirthSalesSwitch$`Batman 2`
SupermanRebirthSwitch <- RebirthSalesSwitch$Superman
SupermanRebirthSwitch2 <- RebirthSalesSwitch$`Superman 2`
WonderWomanRebirthSwitch <- RebirthSalesSwitch$`Wonder Woman`
WonderWomanRebirthSwitch2 <- RebirthSalesSwitch$`Wonder Woman 2`
FlashRebirthSwitch <- RebirthSalesSwitch$`Flash (Barry)`
FlashRebirthSwitch2 <- RebirthSalesSwitch$`Flash (Barry) 2`
NightwingRebirthSwitch <- RebirthSalesSwitch$Nightwing
NightwingRebirthSwitch2 <- RebirthSalesSwitch$`Nightwing 2`

BatmanNew521Switch <- new52Sales1Switch$Batman
BatmanNew521Switch2 <- new52Sales1Switch$`Batman 2`
SupermanNew521Switch <- new52Sales1Switch$Superman
SupermanNew521Switch2 <- new52Sales1Switch$`Superman 2`
WonderWomanNew521Switch <- new52Sales1Switch$`Wonder Woman`
WonderWomanNew521Switch2 <- new52Sales1Switch$`Wonder Woman 2`
FlashNew521Switch <- new52Sales1Switch$`Flash (Barry)`
FlashNew521Switch2 <- new52Sales1Switch$`Flash (Barry) 2`
NightwingNew521Switch <- new52Sales1Switch$Nightwing
NightwingNew521Switch2 <- new52Sales1Switch$`Nightwing 2`
BatmanRebirth1Switch <- RebirthSales1Switch$Batman
BatmanRebirth1Switch2 <- RebirthSales1Switch$`Batman 2`
SupermanRebirth1Switch <- RebirthSales1Switch$Superman
SupermanRebirth1Switch2 <- RebirthSales1Switch$`Superman 2`
WonderWomanRebirth1Switch <- RebirthSales1Switch$`Wonder Woman`
WonderWomanRebirth1Switch2 <- RebirthSales1Switch$`Wonder Woman 2`
FlashRebirth1Switch <- RebirthSales1Switch$`Flash (Barry)`
FlashRebirth1Switch2 <- RebirthSales1Switch$`Flash (Barry) 2`
NightwingRebirth1Switch <- RebirthSales1Switch$Nightwing
NightwingRebirth1Switch2 <- RebirthSales1Switch$`Nightwing 2`
```

```{r}
t.test(BatmanAoCSales, BatmanNew52Sales, alternative="two.sided", conf.level=0.95,paired = FALSE)
t.test(BatmanNew52Sales, BatmanRebirthSales, alternative="two.sided", conf.level=0.95,paired = FALSE)
t.test(BatmanNew52Switch,BatmanNew52Switch2, alternative="two.sided", conf.level=0.95,paired = FALSE)
t.test(BatmanRebirthSwitch,BatmanRebirthSwitch2, alternative="two.sided", conf.level=0.95,paired = FALSE)
t.test(BatmanNew521Switch,BatmanNew521Switch2, alternative="two.sided", conf.level=0.95,paired = FALSE)
t.test(BatmanRebirth1Switch,BatmanRebirth1Switch2, alternative="two.sided", conf.level=0.95,paired = FALSE)
```

```{r}
t.test(SupermanAoCSales, SupermanNew52Sales, alternative="two.sided", conf.level=0.95,paired = FALSE)
t.test(SupermanNew52Sales, SupermanRebirthSales, alternative="two.sided", conf.level=0.95,paired = FALSE)
t.test(SupermanNew52Switch,SupermanNew52Switch2, alternative="two.sided", conf.level=0.95,paired = FALSE)
t.test(SupermanRebirthSwitch,SupermanRebirthSwitch2, alternative="two.sided", conf.level=0.95,paired = FALSE)
t.test(SupermanNew521Switch,SupermanNew521Switch2, alternative="two.sided", conf.level=0.95,paired = FALSE)
t.test(SupermanRebirth1Switch,SupermanRebirth1Switch2, alternative="two.sided", conf.level=0.95,paired = FALSE)
```

```{r}
t.test(WonderWomanAoCSales, WonderWomanNew52Sales, alternative="two.sided", conf.level=0.95,paired = FALSE)
t.test(WonderWomanNew52Sales, WonderWomanRebirthSales, alternative="two.sided", conf.level=0.95,paired = FALSE)
t.test(WonderWomanNew52Switch,WonderWomanNew52Switch2, alternative="two.sided", conf.level=0.95,paired = FALSE)
t.test(WonderWomanRebirthSwitch,WonderWomanRebirthSwitch2, alternative="two.sided", conf.level=0.95,paired = FALSE)
t.test(WonderWomanNew521Switch,WonderWomanNew521Switch2, alternative="two.sided", conf.level=0.95,paired = FALSE)
t.test(WonderWomanRebirth1Switch,WonderWomanRebirth1Switch2, alternative="two.sided", conf.level=0.95,paired = FALSE)
```

```{r}
t.test(FlashAoCSales, FlashNew52Sales, alternative="two.sided", conf.level=0.95,paired = FALSE)
t.test(FlashNew52Sales, FlashRebirthSales, alternative="two.sided", conf.level=0.95,paired = FALSE)
t.test(FlashNew52Switch,FlashNew52Switch2, alternative="two.sided", conf.level=0.95,paired = FALSE)
t.test(FlashRebirthSwitch,FlashRebirthSwitch2, alternative="two.sided", conf.level=0.95,paired = FALSE)
t.test(FlashNew521Switch,FlashNew521Switch2, alternative="two.sided", conf.level=0.95,paired = FALSE)
t.test(FlashRebirth1Switch,FlashRebirth1Switch2, alternative="two.sided", conf.level=0.95,paired = FALSE)
```

```{r}
t.test(NightwingAoCSales, NightwingNew52Sales, alternative="two.sided", conf.level=0.95,paired = FALSE)
t.test(NightwingNew52Sales, NightwingRebirthSales, alternative="two.sided", conf.level=0.95,paired = FALSE)
t.test(NightwingNew52Switch,NightwingNew52Switch2, alternative="two.sided", conf.level=0.95,paired = FALSE)
t.test(NightwingRebirthSwitch,NightwingRebirthSwitch2, alternative="two.sided", conf.level=0.95,paired = FALSE)
t.test(NightwingNew521Switch,NightwingNew521Switch2, alternative="two.sided", conf.level=0.95,paired = FALSE)
t.test(NightwingRebirth1Switch,NightwingRebirth1Switch2, alternative="two.sided", conf.level=0.95,paired = FALSE)
```

